Efficient pedigree recording for fast population genetics simulation

### 2017-11-27 forwards_paper.tex
above -> below
address PLR's comment on tracking selected-vs-neutral variants

To measure the performance gains from ancestry recording, we ran simulations implemented in C++ (see above) with and
without ancestry tracking.  The simulations without ancestry tracking introduced neutral mutations at a scaled mutation
rate equal to the scaled recombination rate (\textit{e.g.}, $\theta = 4N\mu = \rho$, where $\rho = 4Nr$, $N$ is the
diploid population size, $\mu$ is the
mutation rate to neutral mutations (per gamete, per generation) and $r$ is the recombination rate per diploid per
generation.  Both $\mu$ and $r$ are the means of a Poisson process and we used the infinitely-many sites mutation model
\citep{Kimura1969-uc}.

We varied $N \in (1000, 10000, 50000)$, $\rho \in (10^3, 10^4, 10^5)$ and ran a single replicate of all $(N,\rho)$
combinations.  Deleterious mutations were introduced at rate $\rho/100$ per generation, drawing scaled selection
coefficients ($2Ns$)
from a Gamma distribution with a mean of -5 and a shape parameter of 1.  This distribution of fitness effects results in
thousands of weakly-deleterious mutations segregating in the population, many of which drift to intermediate
frequencies.

>>>>

To measure the performance gains from ancestry recording, we ran simulations implemented in C++ (see below) with and
without ancestry tracking.  The simulations without ancestry tracking introduced neutral mutations at a scaled mutation
rate equal to the scaled recombination rate (\textit{e.g.}, $\theta = 4N\mu = \rho$, where $\rho = 4Nr$, $N$ is the
diploid population size, $\mu$ is the
mutation rate to neutral mutations (per gamete, per generation) and $r$ is the recombination rate per diploid per
generation.  Both $\mu$ and $r$ are the means of a Poisson process and we used the infinitely-many sites mutation model
\citep{Kimura1969-uc}.

We varied $N \in (1000, 10000, 50000)$, $\rho \in (10^3, 10^4, 10^5)$ and ran a single replicate of all $(N,\rho)$
combinations.  Deleterious mutations were introduced at rate $\rho/100$ per generation, drawing scaled selection
coefficients ($2Ns$)
from a Gamma distribution with a mean of -5 and a shape parameter of 1.  This distribution of fitness effects results in
thousands of weakly-deleterious mutations segregating in the population, many of which drift to intermediate
frequencies.  The case of many mutations with selection is a non-trivial violation of exchangeability assumptions of the
coalescent \citep{Neuhauser1997-nn}.  Therefore, these selected mutations must be explicitly tracked in our forward simulation
and the time savings due to ancestry tracking come from not having to record \textit{neutral} mutations.
